Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/evaluation.tex
edits

We obtain routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The policies are written in English and serve as a guide for operators when generating configuration templates for the data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).

The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}). The backbone network classifies external neighbors into several different categories and prefers paths through them in order. It does not want to provide transit among certain types of neighbors. For some neighbors, it prefers some links over the others. It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA). Finally, it has filters to prevent bogons (private address space) from external neighbors, accept customer prefixes only from customers, and prevent customers from providing transit to other large networks.

@@

Not counting the lines for various definitions like prefix and customer groups or for ownership constraints that define where routes originate, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.

@@

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
  \end{minipage}
  \caption{Configuration minimization.}
  \label{fig:minipage2}
\end{figure}

We now study the compilation of time for both policies as a function of network size. Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input. For the data center network, we build and provide as input fat tree topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy. We take this approach to smoothly explore different sizes; there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies. For a given size, our reported results match those for the concrete topologies.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
For the data center policy, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel. Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase. No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time. \sysname compiles each data center in under 15 seconds per-prefix on average. Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
%
For the backbone policy, the \sysname compiler scales hundreds of routers, in a little over a minute per-prefix. However, unlike the data center policy, the number of prefixes for the backbone policy stays relatively fixed. Total compilation time for the largest backbone topology tested, with 200 routers, takes less than 3 minutes total. The presence of more preferences in the backbone policy increases the size of the product graph, and means minimization becomes a more expensive step in compilation.

The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.

>>>>

We obtain routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The policies are written in English and guide operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).

The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}). The backbone network classifies external neighbors into several different categories and prefers paths through them in order. It does not want to provide transit among certain types of neighbors. For some neighbors, it prefers some links over the others. It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA). Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent using peers to go through a provider, etc.

@@

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.

@@

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
  \end{minipage}
  \caption{Configuration minimization.}
  \label{fig:config-minimization}
\end{figure}

We now study the compilation of time for both policies as a function of network size. Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input. For the data center network, we build and provide as input fat tree topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy. We take this approach to smoothly explore different sizes. 
%there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies. For a given size, our reported results match those for the concrete topologies.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
For both policies, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel. Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes, broken down by compilation phase. No single compilation phase dominates the running time of the compiler, however construction and minimization of the product graph take the most time. Total compilation for the largest data center takes less than 9 minutes total. Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.

\subsection{Configuration size}

The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. 
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. 
Figure~\ref{fig:config-minimization} shows the effect of minimization for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
